The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-07 manuscript/manuscript.Rnw
fix horse table explanation
add missing \begin{figure}

\begin{table}[h]
  \tiny
<<top.50.horse.expressed.genes,echo=FALSE,results="asis">>=
top.horse.genes <- top.genes.table(species.name="equus caballus")
print(xtable(top.horse.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.horse.genes,"Gene symbol")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes in \horse which are
  not ribosomal, mitochondrial, or whose human ortholog is a
  housekeeping gene}
\label{tab:top50_horse_placenta}
\end{table}

@@

<<rln2.evolution.tree,echo=FALSE,fig.width=12,fig.height=12,warning=FALSE,message=FALSE>>=

>>>>

\begin{table}[h]
  \tiny
<<top.50.horse.expressed.genes,echo=FALSE,results="asis">>=
top.horse.genes <- top.genes.table(species.name="equus caballus")
print(xtable(top.horse.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.horse.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\horse}{tab:all_equus_caballus_placenta}}
\label{tab:top50_horse_placenta}
\end{table}

@@

\begin{figure}
<<rln2.evolution.tree,echo=FALSE,fig.width=12,fig.height=12,warning=FALSE,message=FALSE>>=
